Constructing Statistical Deformable Models with Shape Flow

### 2015-07-16 contents/implementation.tex
Updates from ShareLaTeX

In addition, let .. be the image domain where the reference and training shapes are defined and ... denote the point location. We denote the shape flow result as ...,  where u_n(x) is the displacement vector that matches the point ... of the image of the reference shape with its corresponding location at the image of the $n$-th training shape.

@@

where $\bm{v_i}(\bm{x})$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$. In other words, the shape flow for every point $\bm{x}$ is described as linear combination of basis elements that is controlled by the coefficients $\bm{v_i}(\bm{x})$ that depend on $\bm{x}$.
The values of the $i$-th coefficient for all the points $\bm{v_i}(\bm{x})$ can be interpreted as an image defined on \Omega. Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v_i}(\bm{x})$

>>>>

In addition, let .. be the image domain where the reference and training shapes are defined and ... denote the point location. We denote the shape flow result as ...,  where $u_n(x)$ is the displacement vector that matches the point ... of the image of the reference shape with its corresponding location at the image of the $n$-th training shape.

@@

where $\bm{v_i}(\bm{x})$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$. In other words, the shape flow for every point $\bm{x}$ is described as linear combination of basis elements that is controlled by the coefficients $\bm{v_i}(\bm{x})$ that depend on $\bm{x}$.
The values of the $i$-th coefficient for all the points $\bm{v_i}(\bm{x})$ can be interpreted as an image defined on $\Omega$. Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v_i}(\bm{x})$
